---
title: "Homewwork 5"
author: "Yali Zhai"
date: "11/18/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2 


Import data and create dataframe.

```{r}
path_df = 
  tibble(
    path = list.files("lda-data"),
  ) %>% 
  mutate(
    path = str_c("lda-data/", path),
    data = map(.x = path, ~read.csv(.x))) 

```

Tidy the dataframe.

```{r}
study_tidy_df =
path_df %>%
  separate(path, into = c("group", "id"), sep = "_") %>% 
  mutate(
    group =  str_replace(group, "lda-data/con", "control"),
    group =  str_replace(group, "lda-data/exp", "experiment"),
    id = as.numeric(gsub("[^0-9]", "", id))
  ) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    values_to = "value"
  ) %>% 
  mutate(week = gsub("[^0-9]", "", week))
```


Make a spaghetti plot.

```{r}
study_tidy_df %>% 
  ggplot(aes(x = week, y = value, group = id)) +
  geom_line() + 
  stat_smooth(aes(group = 1)) + 
  stat_summary(aes(group = 1),
    geom = "point", fun = mean, shape = 17, size = 3) + 
  facet_grid(. ~ group)

```

For comparison, I make a smooth line of mean for each group. In the control group, the mean value is stable during the 8 weeks. But in the experiment group, the mean value increases gradually with time.


## Problem 3


```{r}
sim_mean_p = function(n = 30, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    t.test() %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}
```


```{r}
sim_results = 
  tibble(mu_test = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mu_test, ~rerun(5000, sim_mean_p(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  rename(mean = estimate)
```


make a plot of power
```{r}
sim_results %>% 
  group_by(mu_test) %>% 
  summarize(
    sum_rej = sum(p.value < 0.05),
    power = sum_rej/5000
  ) %>% 
  ggplot(aes(x = mu_test, y = power)) +
   geom_bar(stat = "identity")
```

As mu getting larger, the power of the test is larger until reaching 1.



make a plot of average estimate of mean
```{r}
sim_results %>% 
  group_by(mu_test) %>% 
  summarize(
    emp_mean = mean(mean)) %>% 
  ggplot(aes(x = mu_test, y = emp_mean)) +
   geom_bar(stat = "identity")

```

The average estimate of mu is approximately equal to the true value of mu.

Make the plot of the average estimate of mu in samples for which the null was rejected.

```{r}
sim_results %>% 
  filter(p.value < 0.05) %>% 
  group_by(mu_test) %>% 
  summarize(
    rej_mean = mean(mean)) %>% 
  ggplot(aes(x = mu_test, y = rej_mean)) +
   geom_bar(stat = "identity")
```

When mu = 0, the part of estimates of mu which the null is rejected is normally distributed around 0. Thus it average is approximately equal to 0.

When mu > 0, as mu getting larger, the proportion of times the null was rejected is larger, the part that estimates of mu around 0 is smaller, so the average of which the null is rejected is more closer to the true value.
Thus as we can see from the plot, for mu > 3, the sample average of mu across tests for which the null is rejected is approximately equal to the true value of mu.

